A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Proposal improvement

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful (AI) algorithms have previously found their
inspiration. Our focus was not on a single animal species but all of them,
using general abstraction to identify what those species have in common. In our
analysis, we consider a broad animal spectrum, from bacteria to humans and
lions, finding our inspiration on the biological Life Cycle of the animal
species.

>>>>

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their inspiration. Our focus was not on a single animal species but all of
them, using general abstraction to identify what those species have in common.
In our analysis, we consider a broad animal spectrum, from bacteria to humans
and lions, finding our inspiration on the biological Life Cycle of the animal
species.
